---
title: "Test_Code"
author: "Kaylee Carroll"
date: "2022-09-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Exercise Tacocat
Tacocat was defined in a vector. Length functions generalize for any vector.
```{r}
vect1 <-c("t","a","c","o","c","a","t")
vect1 ==vect1[length(vector):1]
```
## Exercise 1: Rows & Columns

The total scores column was assigned a vector called tot_score.

```{r}
tot_score <-Test_V_output$`Total Score`

```

The total score of row 6 was found to be 290 and the molecular reaction was between chk1 and atr.

```{r}
Test_V_output$`Total Score`[6]
```

## Exercise 2: Mean and Standared Deviation

The mean and standard devation of the total scores were found in the set. They were 63.79919 and 55.29295 respectively.

```{r}
mean(tot_score)
sd(tot_score)


```

There were 157 unique PMCIDs.

```{r}
unique(Test_V_Output$Paper.ID)

```

## Exercise 3: Vectorization

The evidence, kind, match scores, and epistemic value columns were combined to get the total scores of the set.

```{r}
new_tot = (Test_V_output$Kind.Score+(Test_V_output$Evidence.Score*Test_V_output$Match.Score))
```

## Exercise 4: Subsets

The locations, cell type, and organsim columns were deleted and the top 100 interactions were scored.

```{r}
Test_V_output<-Test_V_output[,!names(Test_V_output)%in% c("Location","Organism","Cell.Type")]
Test_V_output[1:100,]

```
## Exercise 1: Adding a New Column to Dataset1
Ggplot was downloaded and installed. A new column, called position, was added. A position vs divergence plot was made. 
```{r}
install.packages("ggplot2")
library(ggplot2)
Positions <-(Dataset_S1$start+Dataset_S1$end)/2
Dataset_S1$Positions <-Positions
ggplot(Dataset_S1) + geom_point(aes(x=Positions, y=Divergence))

```
## Exercise 2: Plot Density of Test_V_Output 
Ggplot was installed. The density of Total score was taken. 
```{r}
install.packages("ggplot2")
library(ggplot2)
ggplot(Test_V_output) + geom_density(aes(x=Test_V_output$`Total Score`),fill="black")
```
## Exercise 3: Cut function 
```{r include=TRUE}
TestData$Divergence.binned <- cut(TestData$Divergence, 5)
```


```
## Indexing
list
```{r}
word<-"tacocat"
substr(word,1,1)
substr(word,1,4)
substr(word,1,7)
```

## If/Else Statements

```{r echo=FALSE}
#shirt<-"red"
#shirt<-"yellow"
#shirt<-"green"
#shirt<-"blue"
shirt<-"white"
```
^^ this is to choose the value of 'shirt'
```{r echo=FALSE}
if (shirt=="red") {
  print("Eat apple") 
} else if (shirt=="yellow"){
  print("Eat banana")
} else if (shirt=="green"){
  print("Eat spinach")
} else if (shirt=="blue"){
  print ("Eat blueberries")
} else {
  print ("Eat yogurt")
} 
```

## While Functions

```{r echo=FALSE}
num <- 6
while (num<20){
  num <- num+1
}
```

Example 

```{r}
stop <- sample (1:1000,1)
num <- 1
while (num<stop){
  print("...")
  num <- num+1
}
print("Pop!")
```

## For Functions

```{r echo=FALSE}
vect1 <- c(1,2,3)
for (each in vect1){
  print(each)
}
```

## Graphs

to plot a dataframe column density

```{r include=TRUE}
ggplot(Test_V_output)+ geom_density(aes(x=Total.Score, fill="red"))
```

to plot a dataframe column density with specific restraints -- %in% = only; >, <, !=

```{r include=TRUE}
ggplot(Test_V_output[Test_V_output$Total.Score > 140,])+ geom_density(aes(x=Total.Score, fill="red"))
ggplot(Dataset_S1[Dataset_S1$total.SNPs >70,])+geom_point(aes(x=total.SNPs, y=total.Bases))
```

to plot a bar chart

```{r}
ggplot(TestData) + geom_bar(aes(x=Divergence.binned2))
```

## Binning

new column name <- cut(column to be binned, number of bins needed)
```{r include=TRUE}
TestData$Divergence.binned <- cut(TestData$Divergence, 5)
```
OR
new column name <- cut(column to be binned, c(x, y, z))

```{r include=TRUE}
TestData$Divergence.binned2 <- cut(TestData$Divergence, c(-0.2, 0, 0.02, 0.04, 0.06, 0.08, 0.10, 0.12, 1.6))
```

## Coding Diagrams

For unique paper ID problem

want -- how many unique papers are there in the PaperID colum in Test_V_output?

Note: This is a vector of lists.

1. Remove "junk" characters
  gsub("[", "]", "//', " ", df$PaperIDs)
2. Split up lists of IDs
  SplitPaperIDs <- unlist(strsplit(df$PaperIDs, ","))
3. Revectorize to vector of individual IDs
  vect1 = c()
  for (every in SplitPaperIDs){
    append to vect1
  }
4. Count unique paper IDs
  length(unique(vect1))
  Signs

```{r}
#greater than or equal
x >= 5
#does not equal
x != 5
#equals
5+3==4
```

Types of Values

```{r}
#Numeric 
c(1,2.2,-0.1)
#Integer 
c(1,2,3)
#Character (string)
c("ACTGAC", "or", "hello")
#
```

Boolean

```{r}
#equal to?
5+2== 5
#is it in this
"What" %in% c("Hello", "What")
#is it not equal to 
200-0!=21
#is this not a number
is.nan(0/0)
is.nan(9/0)
#is there nothing in this?
is.null(c())

#list can be different values vector has to be the same values (characters, integers, etc)

```

Making vectors vectors have to have same type of entries. Lists can be heterogenous

```{r}
#vectors with names for each value
vect<- c(a=5,b=4,b=6)
#referencing named value in vector
vect["a"]
# saving normal vector
vector<- c(5,4,6)
#Indexing vector values
vector2 <- c(1,2,3,4,5,6)
vector2[3]
#advanced indexing                           returning from x:y
vector2[1:3]
#reorder
vector2[c(6,5,4,3,2,1)]
#reverse elements
vector2[6:1]
#length function
length()
#substring
string1<- c("abcd")
substr(string1,1,3)
```

DataFrame indexing

```{r}
#referencing a column 
df[,1]
df$nameOfColumn
#Reference row 
df[2,]
#Reference cell
df[2,1]
```

Uploading spreadsheets

```{r}
#CSV
dataframe <- read.csv("//Users//nagendra//Desktop//Bioinformatics//Lecture//Test_V_output.csv", sep=",", header = TRUE )
#TSV
read.csv("//Users//nagendra//Desktop//Bioinformatics//Lecture//FileNAME", sep=" ", header = TRUE )

```

Analyzing data frames

```{r}
mean(vector2)
sd(vector2)
#Counting frequencies in column
sum(dataframe$Total.Score==140)
table(dataframe$Total.Score == 140)

```

Making a new column

```{r}
dataframe$Calc_TotScore <- (dataframe$Kind.Score+(dataframe$Evidence.Score*dataframe$Match.Score))*dataframe$Epistemic.Value
```

Deleting data

```{r}
#columns
df<- subset(dataframe, select = -c(Calc_TotScore))
#rows
dataframeminusrows<- dataframe[1:100,]
dataframe2<-dataframe[c(1,2,3,4,5),]
dataframe112 <- dataframe[-c(1),]
```

Saving dataframe

```{r}
write.csv(dataframe,"//Users//nagendra//Desktop//Bioinformatics//dataframe.csv ")
```

GRAPHING WITH GGPLOT

```{r}
Data_S1 <- read.csv("//Users//nagendra//Desktop//Bioinformatics//Project//Data//Dataset_S1.txt", header = TRUE, sep = ",")
#density plots
ggplot(Data_S1) + geom_density(aes(x=Divergence), fill="black")
#scatter plot
ggplot(Data_S1) + geom_point(aes(x=position, y=diversity)) 
```

Discretization/binning cut(df$column,# of bins) ##or for assigned bins cut(df$column,c(5,10,15,20,25))

```{r}
#histogram
ggplot(Data_S1) + geom_bar(aes(x=BinData2))
```

If/else statement

```{r}
x<-"blue"
if(x=="blue"){
  print("blueberries")
} else if(x=="red"){
  print("apple")
} else if(x=="orange"){
  print("Orange")
} else if(x=="yellow"){
  print("bannana")
}else {
  print("nothing")
}
```

while loops will loop all code withing the while until the condition is met

```{r}
x <- 0
while(x<=999){
print("...")
  x<- sample(1:1000,1)
}
print("pop goes the weasel")
```

For loops

```{r}
PopWeasel <- c("5", "4", "3", "2","1")
for(each in PopWeasel){
  print("hi")
}
```

while and for loop together

```{r}
x<- 1
while(x!=50){
print("wait")
  x<- sample(1:100,1)
  } 
    if(x==50){
      print("done")
    } 
  
```

Solution for lab4

```{r}
for (each in c(length(LEEs):1)){
  if (length(unique(unlist(strsplit(Lab4Data$Paper.ID[each], ",")))) == 1){
    Lab4Data <- Lab4Data[-c(each),]
  }
}
```
## Lab 4: Coding Diagram 
```{r}
MachineRead_output <- read.csv("MachineRead_output.csv")
MachineRead_output$Paper.ID <- gsub("\\[","",MachineRead_output$Paper.ID)
MachineRead_output$Paper.ID <- gsub("\\]","",MachineRead_output$Paper.ID)
MachineRead_output$Paper.ID <- gsub("\\'","",MachineRead_output$Paper.ID)
MachineRead_output$Paper.ID <- gsub(" ","",MachineRead_output$Paper.ID)


paper_ids <-c()
for(each in MachineRead_output$Paper.ID){
paper_ids <- unlist(strsplit(each,","))

row_num <- which(each == MachineRead_output$Paper.ID)

MachineRead_output$number_unique[row_num] <- length(unique(paper_ids))
  
  }
row_to_remove <- which(MachineRead_output$number_unique == 1)
MachineRead_output <-MachineRead_output[-c(row_to_remove),]
```

